A Methodology and Implementation of Automated Emissions Harmonization for Use in Integrated Assessment Models

### 2018-02-05 paper.tex
luc to luluc

%%% Acronyms
\newacronym{sres}{SRES}{Special Report on Emissions Scenarios}
\newacronym{cmip6}{CMIP6}{Coupled Model Intercomparison Project (Phase 6)}
\newacronym{smip}{ScenarioMIP}{Scenario Model Intercomparison Project}
\newacronym{ceds}{CEDS}{Community Emissions Data System}
\newacronym{esm}{ESM}{Earth System Model}
\newacronym{luc}{LUC}{Land-use Change}
\newacronym{luluc}{LULUC}{Land-use and Land-use Change}
\newacronym{weu}{WEU}{Western Europe}
\newacronym{nam}{NAM}{North America}
\newacronym{pao}{PAO}{Pacific OECD}
\newacronym{eeu}{EEU}{Central and Eastern Europe}
\newacronym{fsu}{FSU}{Former Soviet Union}
\newacronym{pas}{PAS}{Other Pacific Asia}
\newacronym{cpa}{CPA}{Centrally-planned Asia and China}
\newacronym{sas}{SAS}{South Asia}
\newacronym{mea}{MEA}{Middle East and North Africa}
\newacronym{afr}{AFR}{Sub-Saharan Africa}
\newacronym{lam}{LAM}{Latin America and the Caribbean}
\newacronym{cli}{CLI}{Command Line Interface}
\newacronym{wmo}{WMO}{World Meteorological Organization}

@@

The global climate change community has recently developed a new global
historical emissions data set for both anthropogenic emissions (i.e., the
\gls{ceds} \cite{hoesly_historical_2017} and open-burning \gls{luluc} emissions
\cite{van_marle_historic_2017}) which, in conjunction with the \gls{ssp}
\gls{iam} trajectories, will be used for climate-related modeling exercises of
\gls{cmip6}.

@@

However, other concerns may lead to a better-informed choice than using a
blanket method for all emissions trajectories. For example, emissions from
\gls{luluc} are known to have high year-to-year variation, and therefore
historical data may change drastically depending on the base year considered. In
such a situation, a method that converges at a year past the modeled time period
is a better choice in order to smooth out discrepancies between the historical
data used to develop model and the new data source being used for harmonization.

>>>>

%%% Acronyms
\newacronym{sres}{SRES}{Special Report on Emissions Scenarios}
\newacronym{cmip6}{CMIP6}{Coupled Model Intercomparison Project (Phase 6)}
\newacronym{smip}{ScenarioMIP}{Scenario Model Intercomparison Project}
\newacronym{ceds}{CEDS}{Community Emissions Data System}
\newacronym{esm}{ESM}{Earth System Model}
\newacronym{luc}{LULUC}{Land-use and Land-use Change}
\newacronym{weu}{WEU}{Western Europe}
\newacronym{nam}{NAM}{North America}
\newacronym{pao}{PAO}{Pacific OECD}
\newacronym{eeu}{EEU}{Central and Eastern Europe}
\newacronym{fsu}{FSU}{Former Soviet Union}
\newacronym{pas}{PAS}{Other Pacific Asia}
\newacronym{cpa}{CPA}{Centrally-planned Asia and China}
\newacronym{sas}{SAS}{South Asia}
\newacronym{mea}{MEA}{Middle East and North Africa}
\newacronym{afr}{AFR}{Sub-Saharan Africa}
\newacronym{lam}{LAM}{Latin America and the Caribbean}
\newacronym{cli}{CLI}{Command Line Interface}
\newacronym{wmo}{WMO}{World Meteorological Organization}

@@

The global climate change community has recently developed a new global
historical emissions data set for both anthropogenic emissions (i.e., the
\gls{ceds} \cite{hoesly_historical_2017} and open-burning \gls{luc} emissions
\cite{van_marle_historic_2017}) which, in conjunction with the \gls{ssp}
\gls{iam} trajectories, will be used for climate-related modeling exercises of
\gls{cmip6}.

@@

However, other concerns may lead to a better-informed choice than using a
blanket method for all emissions trajectories. For example, emissions from
\gls{luc} are known to have high year-to-year variation, and therefore
historical data may change drastically depending on the base year considered. In
such a situation, a method that converges at a year past the modeled time period
is a better choice in order to smooth out discrepancies between the historical
data used to develop model and the new data source being used for harmonization.
